Revisiting the Austral Spring Extratropical Southern Hemisphere zonally asymmetric circulation using complex Empirical Orthogonal Functions

### 2022-03-21 analysis/paper/shceof.Rmd
Agrega detalle a los estudios de cEOF

An alternative methodology that has been proposed to study travelling and standing waves is complex Empirical Orthogonal Functions [@horel1984].
This method extends EOF analysis to capture oscillations with varying amplitude and phase and has been applied to the time domain on water level to study tide-river interactions [@laurel-castillo2020] and temperature and precipitation anomalies [e.g. @krokhin2007; @gelbrecht2018].
To our knowledge, complex EOF has not been applied in the spatial domain to capture the phase-varying nature of planetary waves.

>>>>

An alternative methodology that has been proposed to study travelling and standing waves is complex Empirical Orthogonal Functions [@horel1984].
This method extends EOF analysis to capture oscillations with varying amplitude and phase and has been applied to the time domain. For instance, 
@krokhin2007 applied cEOF to station-based monthly precipitation anomalies and monthly temperature anomalies in the Eastern Siberia and the Far East region to characterise the main modes of variability and their connection to teleconnection indices. 
Similarly, @gelbrecht2018 used cEOF applied to daily precipitation from reanalysis to study the propagating characteristics of the South American Monsoon. 
To our knowledge, complex EOF has not been applied in the spatial domain to capture the phase-varying nature of planetary waves.
